A Longitudinal Analysis of the Privacy Paradox

### 2020-05-07 manuscript.RmD
- added e-mail addresses
- updated pdf

---
title             : "A Longitudinal Analysis of the Privacy Paradox" 
shorttitle        : "Longitudinal Analysis of the Privacy Paradox"
author:            
  - name          : "Tobias Dienlin"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
    corresponding : yes
  - name          : "Philipp K. Masur"
    affiliation   : "2"
  - name          : "Sabine Trepte"
    affiliation   : "1"
affiliation:

@@

  This manuscript features a companion website that includes detailed summaries of the statistical results, the code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy-paradox-longitudinal). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective. We differentiate between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  People who were more concerned than usual also shared slightly less information than usual (within-person level). 
  We found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  The results provide further evidence against the privacy paradox, but more research is needed to better understand the variables' potential causal relation.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [bibliography/references.bib]
  - [bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines; comment lines after "output: html_document ..."
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

>>>>

---
title             : "A Longitudinal Analysis of the Privacy Paradox" 
shorttitle        : "Longitudinal Analysis of the Privacy Paradox"
author:            
  - name          : "Tobias Dienlin"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
    corresponding : yes
  - name          : "Philipp K. Masur"
    email         : "philipp.masur@uni-mainz.de"
    affiliation   : "2"
  - name          : "Sabine Trepte"
    email         : "sabine.trepte@uni-hohenheim.de"
    affiliation   : "1"
affiliation:

@@

  This manuscript features a companion website that includes detailed summaries of the statistical results, the code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy-paradox-longitudinal). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective. We differentiate between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  People who were more concerned than usual also shared slightly less information than usual (within-person level). 
  We found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  The results provide further evidence against the privacy paradox, but more research is needed to better understand the variables' potential causal relation.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [bibliography/references.bib]
  - [bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines; comment lines after "output: html_document ..."
output            : papaja::apa6_pdf
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#     toc_depth: 2
---
